\documentclass[margin]{res}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{url}
\textwidth=5.2in        % The text width of the section headings.

\begin{document}
\name{Keith Yong\\[15pt]}

\address{{\bf Address}\\346 Nicholas Ct \\Wilmington, DE 19808\\(302) 887-0387}
\address{{\bf Links}\\\url{terda12@gmail.com}\\\url{github.com/keithyong}\\\url{keithy.me}}

\begin{resume}

\section{Education}
University of Delaware\\
Computer Science BS\\
Graduating December 2016

\section{Work}
\textit{Conferency (2015)} - Worked as a full stack web developer for a startup. Built various features for a multipage web application in Flask. Worked on creating new REST API endpoints. Built various front-end templates out of Jinja2 and Bootstrap. Created CSS for the landing page and navbars. Used a Git workflow system of branching and pull requests.

\section{Projects}

Find my web projects at \underline{\url{keithy.me}}\\
\textit{pstmin (2016)}\\ Created a minimalist pastebin.com clone written in Golang. \underline{\texttt{\href{http://www.pstmin.com}{Demo}}}

\textit{moolist (2016)}\\ Created a persistent todo list with React and Redux. Uses server side rendering to increase initial render time. \underline{\texttt{\href{http://http://moolist.keithy.me}{Demo}}}

\textit{Reddit Clone (2015)}\\ Created a \texttt{reddit.com} clone. Used React as the primary front end framework, and created React components such as \texttt{Post.jsx} and \texttt{Comment.jsx} to avoid DRY. Designed a full SQL schema to handle posts, comments, upvotes, and other features. Used PostgresQL trigger functions to handle efficient upvoting. Utilized webpack to bundle up all dependencies into several \texttt{bundle.js} files. \underline{\texttt{\href{https://github.com/keithyong/pyramus}{Github}}} \underline{\texttt{\href{http://pyramus.keithy.me}{Demo}}}

% \textit{Realtime Chat Room (February 2015)}\\ Wrote a real-time online chatroom using a React frontend, and socket.io, Node, and postgresQL backend. \underline{\texttt{\href{https://github.com/keithyong/chat-room}{Github}}} \underline{\texttt{\href{http://chatter.keithy.me}{Demo}}}

% \textit{Pomodoro Timer (January 2015)}\\ Wrote an online pomodoro timer in pure Javascript and CSS with a focus on UX and design. Used CSS media queries to ensure a mobile ready responsive experience. \underline{\texttt{\href{https://github.com/keithyong/pomodoro}{Github}}} \underline{\texttt{\href{http://keithy.me/pomodoro}{Demo}}}


\textit{Online Fibonacci Calculator (December 2014)}\\ Wrote an online nth-Fibonacci calculator in Javascript. Gives the users a choice to calculate using dynamic programming or recursion, and notifies them of the running time. Wrote an explanation under the calculator which analyzes how dynamic programming significantly reduces running time. Used D3.js and media queries to make mobile responsive recursion tree visuals. \underline{\texttt{\href{https://github.com/keithyong/fibonacci-calc}{Github}}} \underline{\texttt{\href{http://keithy.me/fibonacci-calc}{Demo}}}

\section{Languages}
Great - Javascript, Node.js, React.js, PostgreSQL/MySQL, CSS

Familiar - Python, Golang, C, C++, LaTeX

\section{Courses}
Data Structures \& Algorithms, Computer Architecture, Operating Systems, SQL, Advanced Web Technologies
\end{resume}

\end{document}
